-

### 2023-01-20 DRAFT_homogeneous_impact_areas.Rmd
feat: new bbox

<!-- Continue from here after fixing ea_spread -->
```{r, warning=F}
infra_agg_discrete_vect <- eaTools::ea_homogeneous_area(infra_agg_discrete)
```

@@

```{r}
infra_agg_discrete_vect_trd <- st_crop(infra_agg_discrete_vect, myBB)
```

>>>>

<!-- Continue from here after fixing  ea_homogeneous_area -->
```{r, warning=F}
infra_agg_discrete_vect <- eaTools::ea_homogeneous_area(infra_agg_discrete, groups = infrastructureIndex)
```

@@

```{r}
myBB <- st_bbox(c(xmin=260520.12, xmax = 278587.56,
                ymin = 7032142.5, ymax = 7045245.27),
                crs = st_crs(infra_agg_discrete_vect))

infra_agg_discrete_vect_trd <- st_crop(infra_agg_discrete_vect, myBB)
```
